### 2017-09-30 TF-vldb2018/sec-expt.tex

\vspace{-0.2ex}
\stitle{Experimental Settings.} We use the following settings.

@@

\ni (3) We also used real-life dataset \youtube~\cite{youtubeWeb} (see~\cite{fullvldb18}).

@@

%\subsection{Experimental Results}

\stitle{Experimental Results.} In all the experiments, we set $k=10$, $r=2$, $h=3$, $(|V_{P}|,$ $|E_{P}|)$ to be (10,12),
and capacity bounds to be [1,10] by default.
When generating synthetic graphs, we fixed $n=10^7$, $d=10$ and $l=200$.
\looseness=-1
%All the findings on \youtube are reported in the Appendix.

>>>>

\subsection{Experimental Settings}

 We used the following settings.

@@

\ni (3) We also used real-life dataset \youtube~\cite{youtubeWeb}. The description of the dataset can be found in the full version~\cite{fullvldb18}.

@@

\subsection{Experimental Results}

We present our findings. In all the experiments, we set $k=10$, $r=2$, $h=3$, $(|V_{P}|,$ $|E_{P}|)$ to be (10,12),
and capacity bounds to be [1,10] by default.
When generating synthetic graphs, we fixed $n=10^7$, $d=10$ and $l=200$.
All the findings on \youtube are reported in the Appendix.
